Integrative forecasting of seasonal influenza A/H3N2 by genotype and phenotype

### 2019-09-05 manuscript/main.tex
Clean up math notation
Convert capital X's to lowercase bolded x's, etc. Still to do is replacement of
these characters with custom math terms.

As in \cite{Luksza:2014hj}, we assumed that influenza A/H3N2 populations can be described by an exponential growth model.
Under this model, we estimated the future frequency of the global population, $\hat{X}$, at some time in the future, $t + \Delta{t}$, based on the current frequency, $x_{i}(t)$, and fitness, $f_{i}(t)$, of each sample $i$ as follows where the resulting future frequencies were normalized to one by $\frac{1}{Z(t)}$.

$$
\hat{X}(t + \Delta{t}) = \frac{1}{Z(t)}\sum_{i}x_{i}(t)\exp(f_{i}(t))
$$

We defined the fitness of each sample at time $t$ as the additive combination of one or more fitness metrics, $f_{i,m}$, scaled by fitness coefficients, $\beta_{m}$.

@@

$$
\Delta(X(u), \hat{X}(u)) = \frac{\sum_{i}\sum_{j}x_{i}(t)\exp(f_{i}(t)\Delta{t})x_{j}(u)d_{i,j} - \sum_{j}\sum_{k}x_{j}(u)x_{k}(u)d_{j,k}}{\sum_{i}\sum_{j}x_{i}(t)x_{j}(u)d_{i,j}}.
$$

>>>>

As in \cite{Luksza:2014hj}, we assumed that influenza A/H3N2 populations can be described by an exponential growth model.
Under this model, we estimated the future frequency of the global population, $\mathbf{\hat{x}}$, at some time in the future, $t + \Delta{t}$, based on the current frequency, $x_{i}(t)$, and fitness, $f_{i}(t)$, of each sample $i$ as follows where the resulting future frequencies were normalized to one by $\frac{1}{Z(t)}$.

$$
\mathbf{\hat{x}}(t + \Delta{t}) = \frac{1}{Z(t)}\sum_{i}x_{i}(t)\exp(f_{i}(t))
$$

We defined the fitness of each sample at time $t$ as the additive combination of one or more fitness metrics, $f_{i,m}$, scaled by fitness coefficients, $\beta_{m}$.
For example, the following equation estimates fitness per sample by epitope cross-immunity ($\mathrm{ep}$), non-epitope mutations ($\mathrm{ne}$), and local branching index ($\mathrm{lbi}$).

$$
f_{i}(t) = \beta_{\mathrm{ep}}f_{i, \mathrm{ep}}(t) + \beta_{\mathrm{ne}}f_{i, \mathrm{ne}}(t) + \beta_{\mathrm{lbi}}f_{i, \mathrm{lbi}}(t)
$$

@@

$$
\Delta\mathbf{d} = \frac{\mathbf{d}(\hat{u}, u) - \mathbf{d}(u, u)}{\mathbf{d}(t, u)}
                                           = \frac{\sum_{i}\sum_{j}x_{i}(t)\exp(f_{i}(t)\Delta{t})x_{j}(u)d_{i,j} - \sum_{j}\sum_{k}x_{j}(u)x_{k}(u)d_{j,k}}{\sum_{i}\sum_{j}x_{i}(t)x_{j}(u)d_{i,j}}.
$$
